\thesistitle

### 2019-07-24 sections/clonerefactor.tex
The equation

\begin{equation}\label{eq:sumequality}
\frac{|{(3,4), (1,8), (7,9)}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
\end{equation}

@@

\subsubsection{Detect Clones on Graph}
\todo{TODO}
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}

>>>>

\begin{equation}\label{eq:sumequality}
\frac{|\{(3,4), (1,8), (7,9)\}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
\end{equation}

@@

Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary. This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way.
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}

\subsubsection{Detect Clones on Graph}
\todo{TODO}
